---
title: "Survey of Affect, Cognition, and Behavior"
output: html_document
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "left")
df <- read.csv(ipath, stringsAsFactors=FALSE)
options(knitr.duplicate.label = "allow")

library(rmarkdown)
library(rsconnect)
library(ggplot2)
```
<br>

## How **happy** are you right now?
<br>
```{r plot, echo = FALSE, message = FALSE, warning =FALSE}

ggplot(df, aes(x=X, y=Happy)) + 
  geom_point() + 
  geom_smooth(method = "loess", se=FALSE, span = 1.6, size = 1.8) +
  labs(x= "Time (days)", y = "Happiness rating") +
  ylim(0,100) +
  theme_classic() + theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))

```
<br><br><br>

## How **sad** are you right now? 
<br>
```{r plot2, echo=FALSE, message = FALSE, warning =FALSE}
ggplot(df, aes(x=X, y=Sad)) + 
  geom_point() + 
  geom_smooth(method = "loess", se=FALSE, span = 1.6, size = 1.8) +
  labs(x= "Time (days)", y = "Sadness rating") +
  ylim(0,100) +
  theme_classic()+ theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))
```
<br><br><br>

## How **stressed** are you right now?
<br>
```{r plot3, echo=FALSE, message = FALSE, warning =FALSE}
ggplot(df, aes(x=X, y=Stressed)) + 
  geom_point() + 
  geom_smooth(method = "loess", se=FALSE, span = 1.6, size = 1.8) +
  labs(x= "Time (days)", y = "Stress rating") +
  ylim(0,100) +
  theme_classic()+ theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))
```
<br><br><br>

## How **relaxed** are you right now?
<br>
```{r plot4, echo=FALSE, message = FALSE, warning =FALSE}
ggplot(df, aes(x=X, y=Relaxed)) + 
  geom_point() + 
  geom_smooth(method = "loess", se=FALSE, span = 1.6, size = 1.8) +
  labs(x= "Time (days)", y = "Relaxation rating") +
  ylim(0,100) +
  theme_classic()+ theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))
```
<br><br><br>

## How much are you **overthinking** right now?
<br>
```{r plot5, echo=FALSE, message = FALSE, warning =FALSE}
ggplot(df, aes(x=X, y=Overthinking)) + 
  geom_point() + 
  geom_smooth(method = "loess", se=FALSE, span = 1.6, size = 1.8) +
  labs(x= "Time (days)", y = "Overthinking rating") +
  ylim(0,100) +
  theme_classic()+ theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))
```
<br><br><br>

## How **optimistic** are you right now?
<br>
```{r plot6, echo=FALSE, message = FALSE, warning =FALSE}
ggplot(df, aes(x=X, y=Optimistic)) + 
  geom_point() + 
  geom_smooth(method = "loess", se=FALSE, span = 1.6, size = 1.8) +
  labs(x= "Time (days)", y = "Optimism rating") +
  ylim(0,100) +
  theme_classic()+ theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))
```
<br><br><br>

## How **self conscious** are you right now?
<br>
```{r plot7, echo=FALSE, message = FALSE, warning =FALSE}
ggplot(df, aes(x=X, y=Self.Conscious)) + 
  geom_point() + 
  geom_smooth(method = "loess", se=FALSE, span = 1.6, size = 1.8) +
  labs(x= "Time (days)", y = "Self consciousness rating") +
  ylim(0,100) +
  theme_classic()+ theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))
```
<br><br><br>

## How much are you **thinking about the past** right now?
<br>
```{r plot8, echo=FALSE, message = FALSE, warning =FALSE}
ggplot(df, aes(x=X, y=Past)) + 
  geom_point() + 
  geom_smooth(method = "loess", se=FALSE, span = 1.6, size = 1.8) +
  labs(x= "Time (days)", y = "Past rating") +
  ylim(0,100) +
  theme_classic()+ theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))
```
<br><br><br>

## How much are you **socializing** right now?
<br>
```{r plot9, echo=FALSE, message = FALSE, warning =FALSE}
ggplot(df, aes(x=X, y=Socializing)) + 
  geom_point() + 
  geom_smooth(method = "loess", se=FALSE, span = 1.6, size = 1.8) +
  labs(x= "Time (days)", y = "Social rating") +
  ylim(0,100) +
  theme_classic()+ theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))
```
<br><br><br>

## How much are you **working out** right now?
<br>
```{r plot10, echo=FALSE, message = FALSE, warning =FALSE}
ggplot(df, aes(x=X, y=WorkingOut)) + 
  geom_point() + 
  geom_smooth(method = "loess", se=FALSE, span = 1.6, size = 1.8) +
  labs(x= "Time (days)", y = "Work out rating") +
  ylim(0,100) +
  theme_classic()+ theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))
```
<br><br><br>

## How much are you **laughing** right now?
<br>
```{r plot11, echo=FALSE, message = FALSE, warning =FALSE}
ggplot(df, aes(x=X, y=Laughing)) + 
  geom_point() + 
  geom_smooth(method = "loess", se=FALSE, span = 1.6, size = 1.8) +
  labs(x= "Time (days)", y = "Laughter rating") +
  ylim(0,100) +
  theme_classic()+ theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))
```
<br><br><br>

## How much are you **procrastinating** right now?
<br>
```{r plot12, echo=FALSE, message = FALSE, warning =FALSE}
ggplot(df, aes(x=X, y=Procrastinating)) + 
  geom_point() + 
  geom_smooth(method = "loess", se=FALSE, span = 1.6, size = 1.8) +
  labs(x= "Time (days)", y = "Procrastination rating") +
  ylim(0,100) +
  theme_classic()+ theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))
```


